Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-02-18 reportTII-ArticleHIL.tex
Report template updated

\usepackage[list=true,labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\graphicspath{%
  {figs/ipe/}
  {figs/dia/}
  {figs/matlab/}
  {figs/imag/}
}

@@

\usepackage{tikz}
\usetikzlibrary{positioning,fit}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \centering
    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesAStuff}
    \caption{}
    \label{fig:fleet}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \centering
    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesSteering}
    \caption{}
    \label{fig:steerSystem}
  \end{subfigure}
  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerSystem} steering model setup (courtesy of AutonomouStuff). }
  \label{fig:AstuffFleetSteeringSetup}
\end{figure}

@@

 Authors in~\cite{Hussain2011} illustrates identification of multiple-input
 single-output model for maximum power point tracking of photovoltaic system. A
 significant effort was conducted to model the photovoltaic system, where the two inputs were
 Solar irradiance and Cell temperature, and the output was DC current. To model
 this system, Matlab’s System Identification Toolbox was used. In order to
 create different models, they collected and used data from an energy center in
 Malaysia. After generating different models, the authors ended up going with a
 fourth order ARX (also known as ARXQS) model because it was the most accurate,
 with a best fit percentage of 93.42\%. The polynomial model equation for ARX is
 shown below. %
 %
 \begin{align*}
   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
 \end{align*}
% 
$y(t)$ is the system output at time $t,$ while $u(t)$ is the input. The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.

@@

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in Fig.~\ref{fig:subFunctionalBlock}. Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem. Some of the systems are multiple output and some are single output as depicted in Fig.~\ref{fig:subFunctionalBlock}. %
%
\begin{figure}[htb]
    \centering 
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
  \caption{}
  \label{fig:steeringmodelarchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
  \caption{}
  \label{fig:brakeModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\textwidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
  \caption{}
  \label{fig:accelerationModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
  \caption{}
  \label{fig:shiftModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
  \caption{}
  \label{fig:speedControlModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
  \caption{}
  \label{fig:speedModelArchitecture}
\end{subfigure}
\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
\label{fig:subFunctionalBlock}
\end{figure}
%

 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
    \caption{Steering block diagram}
    \label{fig:steeringModelBlockDiagram}
\end{figure}

  \subsection{Brake Subsystem}
  The brake subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs. Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed. This boolean value indicates to the user whether or not the brake pedal is being pressed. The brake subsystem is another example of a multiple-input multiple-output system. 
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Brake subsystem block diagram}
    \label{fig:brakeModelArchitecture}
\end{figure}

@@

\begin{figure}[htb]
   \centering 
\begin{subfigure}[b]{0.48\linewidth}
 \centering 
 \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
 \caption{}
 \label{fig:steeringmodelarchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
 \centering
 \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
 \caption{}
 \label{fig:brakeModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\textwidth}
 \centering 
 \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
 \caption{}
 \label{fig:accelerationModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
 \centering 
 \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
 \caption{}
 \label{fig:shiftModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\linewidth}
 \centering
 \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
 \caption{}
 \label{fig:speedControlModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
 \centering
 \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
 \caption{}
 \label{fig:speedModelArchitecture}
\end{subfigure}
\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
\label{fig:subFunctionalBlock}
\end{figure}

>>>>

\usepackage[list=true,labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\graphicspath{%
  {figs/matlab/}
}

@@

\usepackage{tikz}
% \usetikzlibrary{calc,tikzmark}
\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.40\linewidth}
    \centering
    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesAStuff}
    \caption{}
    \label{fig:fleet}
  \end{subfigure}
  \begin{subfigure}[b]{0.40\linewidth}
    \centering
    \includegraphics[height=3.5cm]{figs/img/autonomousVehiclesSteering}
    \caption{}
    \label{fig:steerSystem}
  \end{subfigure}
  \caption{\subref{fig:fleet} Autonomous vehicle fleet in AutonomouStuff Solutions and \subref{fig:steerSystem} steering model setup (courtesy of AutonomouStuff). }
  \label{fig:AstuffFleetSteeringSetup}
\end{figure}

@@

 Authors in~\cite{Hussain2011} illustrates identification of multiple-input
 single-output model for maximum power point tracking of photovoltaic system. A
 significant effort was conducted to model the photovoltaic system, where the two inputs were
 Solar irradiance and Cell temperature, and the output was DC current. To model
 this system, Matlab’s System Identification Toolbox was used. In order to
 create different models, they collected and used data from an energy center in
 Malaysia. After generating different models, the authors ended up going with a
 fourth order ARX (also known as ARXQS) model because it was the most accurate,
 with a best fit percentage of 93.42\%. The polynomial model equation for ARX is
 shown below. %
 %
 \begin{multline*}
   y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = \\
   b_{1}u_{1}(t-n_{k})+...+b_{nb}u_{nb}(t - n_{k}-n_{b}+1) + e(t), 
 \end{multline*}
% 
$y(t)$ is the system output at time $t,$ while $u(t)$ is the input. The noise disturbance of the system is represented by $e(t).$ The variables $na,$ $nb,$ and $nk$ are the system’s number of poles, amount of $b$ parameters, and the samples before the inputs begin to affect the system’s output.

@@

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems as shown in Fig.~\ref{fig:subFunctionalBlock}. Each of the six subsystems can be described as a multiple input system because there are two torque voltage signals used to describe the behavior of each vehicle subsystem. Some of the systems are multiple output and some are single output as depicted in Fig.~\ref{fig:subFunctionalBlock}. %
%
\begin{figure}[htbp]
  \centering
  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
  \label{fig:highLevelSystemArchitecture}
\end{figure}
% \begin{figure}[htb]
%     \centering 
% \begin{subfigure}[b]{0.48\linewidth}
%   \centering 
%   \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
%   \caption{}
%   \label{fig:steeringmodelarchitecture}
% \end{subfigure}
% \\
% \begin{subfigure}[b]{0.48\linewidth}
%   \centering
%   \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
%   \caption{}
%   \label{fig:brakeModelArchitecture}
% \end{subfigure}
% \\
% \begin{subfigure}[b]{0.48\textwidth}
%   \centering 
%   \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
%   \caption{}
%   \label{fig:accelerationModelArchitecture}
% \end{subfigure}
% \begin{subfigure}[b]{0.48\linewidth}
%   \centering 
%   \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
%   \caption{}
%   \label{fig:shiftModelArchitecture}
% \end{subfigure}
% \\
% \begin{subfigure}[b]{0.48\linewidth}
%   \centering
%   \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
%   \caption{}
%   \label{fig:speedControlModelArchitecture}
% \end{subfigure}
% \begin{subfigure}[b]{0.48\linewidth}
%   \centering
%   \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
%   \caption{}
%   \label{fig:speedModelArchitecture}
% \end{subfigure}
% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
% \label{fig:subFunctionalBlock}
% \end{figure}
% %

\subsection{Steering Subsystem}
\label{sec:steeringSubsystem}

The steering subsystem consists of steering, the power steering motors, $\ldots$ The ultimate goal of this subsystem is to control the steering angle for the vehicle to navigate in the desired heading. Therefore, the control system is designed to produce appropriate voltages to be applied to the power steering motors for the steering orient in the target direction. The block diagram of the control system designed for this subsystem is shown in Fig.~

\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
    \tikzstyle{sum} = [draw, circle,fill=orange!15]
    % place nodes
    \node[sum](sum){$\sum$};
    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};

    % Connections
    \draw[stealth-,thick]
    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
    \draw[-stealth,thick]
    (sum.east)--node[midway,above]{Error}(steeringController);
    \draw[-stealth,thick]
    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
    \draw[-stealth,thick]
    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
    \draw[-stealth,thick]
    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
    \fill
    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
    \draw[-stealth,thick]
    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};

  \end{tikzpicture}
  % \captionsetup{justification=centering, margin=3cm}
  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
  \caption{Steering subsystem block diagram.}
  \label{fig:steeringModelBlockDiagram}
\end{figure}

  \subsection{Brake Subsystem}
  The brake subsystem takes the Brake Pedal Pressure Voltages, Brake Pedal Stroke Voltages, and the Brake Pedal On/Off Switch values as inputs. Using these values, it generates a new Brake Pedal Position and a boolean value called Brake Pressed. This boolean value indicates to the user whether or not the brake pedal is being pressed. The brake subsystem is another example of a multiple-input multiple-output system. 
 \begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};

    % Connections
    \draw[stealth-,thick]
    (brakeSubsystem.150)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
    \draw[stealth-,thick]
    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
    \draw[stealth-,thick]
    (brakeSubsystem.-150)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
    \draw[-stealth,thick]
    (brakeSubsystem.15)--node[pos=0.5,above]{Pedal position}++(1.7,0);
    \draw[-stealth,thick]
    (brakeSubsystem.-15)--node[pos=0.5,below]{Brake pressed}++(1.7,0);

  \end{tikzpicture}
    % \captionsetup{justification=centering, margin=3cm}
    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Brake subsystem block diagram}
    \label{fig:brakeModelArchitecture}
\end{figure}

@@

% \begin{figure}[htb]
%    \centering 
% \begin{subfigure}[b]{0.48\linewidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
%  \caption{}
%  \label{fig:steeringmodelarchitecture}
% \end{subfigure}
% \begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
%  \caption{}
%  \label{fig:brakeModelArchitecture}
% \end{subfigure}
% \\
% \begin{subfigure}[b]{0.48\textwidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
%  \caption{}
%  \label{fig:accelerationModelArchitecture}
% \end{subfigure}
% \begin{subfigure}[b]{0.48\linewidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
%  \caption{}
%  \label{fig:shiftModelArchitecture}
% \end{subfigure}
% \\
% \begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
%  \caption{}
%  \label{fig:speedControlModelArchitecture}
% \end{subfigure}
% \begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
%  \caption{}
%  \label{fig:speedModelArchitecture}
% \end{subfigure}
% \caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
% \label{fig:subFunctionalBlock}
% \end{figure}
